% LaTeX resume using res.cls
\documentclass[line,margin]{res}

% Changed margins to fit things
\addtolength{\oddsidemargin}{-.3in}
\addtolength{\evensidemargin}{-.3in}
\addtolength{\textwidth}{0.6in}

\addtolength{\topmargin}{-.2in}
\addtolength{\textheight}{0.4in}

\begin{document}
\name{Richard Hwang}
\address{673 Brannan Street Unit 315, San Francisco CA 94107}
\address{(973) 647-5056 $|$ richard.hwang201@gmail.com}

\begin{resume}
\section{EDUCATION}
{\bf University of California, Berkeley} \hfill {\small May 2014}\\
{\sl Bachelor of Science,} Electrical Engineering and Computer Science \hfill GPA: 3.574

\section{RELEVANT \\ COURSEWORK}
SICP, Data Structures, Machine Structures, Discrete Math and Probability,
Calculus, Linear Algebra, Networking, Security, Compilers, Algorithms,
Artificial Intelligence, Machine Learning, Computer Vision*, Behavioral Data Mining,
Feedback Control Systems*, Quantum Mechanics \\
{\small \textasteriskcentered \  Fall 2013 coursework.}

\section{EXPERIENCE}
{\bf Applications Developer} \hfill {\small July 2014 - Present} \\
{\it C3 Energy}
\begin{itemize} \itemsep -1pt
  \item Foo 
\end{itemize}

{\bf Avionics Software Intern} \hfill {\small May 2013 - August 2013} \\
{\it Space Exploration Technologies}
\begin{itemize} \itemsep -1pt
  \item Developed a tool to help REs analyze telemetry as frequencies across all
      similar tests.
  \item Implemented grouping for telemetry metadata database and front-end visualization.
\end{itemize}

{\bf Teaching Assistant} \hfill {\small Jan 2013 - Present} \\
{\it EECS UC Berkeley}
\begin{itemize}  \itemsep -1pt
  \item Lead two labs and discussions for Structure and Interpretation
      of Computer Programs.
  \item Hold office hours and review sessions, and write homeworks, labs,
      discussions, exams.
\end{itemize}

{\bf Software Engineering Intern} \hfill {\small May 2012 - August 2012} \\
{\it Linkedin}
\begin{itemize}  \itemsep -1pt
  \item Wrote a Python automated test framework for mobile i18n translations.
  \item Created auto-deployment for tablet server with mentor and co-intern in Python.
  \item Hacked an internal employee route finder using Neo4j Graph DB and Ruby on Rails.
\end{itemize}

\section{PROJECTS}
{\bf Some Artificial Intelligence Projects}
\begin{itemize} \itemsep - 1pt
  \item Implemented "Tour Into the Picture", generating all camera views from
    a single picture using homographies, under simplified room assumptions.
  \item Reconstructed 3d object from two pictures with different viewpoints.
  \item Created a classifier that could determine the dominant texture of an image.
  \item Implemented linear regression with s.g.d on one million Amazon reviews.
  \item Implemented decision trees, random forests, and AdaBoost for spam
      classification.
  \item Analyzed political content on Weibo and clustered to find most
      influential users.
  \item Generated eigenfaces using PCA to quickly find similar faces amongst
      students and celebs.
\end{itemize}

{\bf Compiler for Python-like Language}
\begin{itemize} \itemsep - 1pt
  \item Wrote a lexer and parser for a statically-typed Python-like language,
      using Bison and Flex.
  \item Performed type inference and semantic rewrites of the abstract
      syntax tree.
  \item Generated code in C++, dealing with Python specific features, such as
      dicts, closures, etc.
\end{itemize}

\section{COMPUTER \\ SKILLS}
{\sl{\bf Languages \& Tools}: }Python, Matlab, Java, C, Javascript, Git,
    Vim, \LaTeX \\
{\sl{\bf Operating Systems}:} OS X, Linux, Windows.

\section{ACTIVITIES}
Industrial Relations Chair, {\it HKN - EECS Honor Society}
    \hfill {\small January 2012 - December 2012}\\
Organized infosessions, tech talks, and other events between software companies and students.

Emergency Medical Technician, {\it Parsippany Volunteer Ambulance Squad}
    \hfill {\small January 2008 - August 2013}\\
Assessed, treated, and transported patients during 12-hour and 24-hour shifts.

\end{resume}
\end{document}
